### 2020-02-14 README.Rmd
fix the description of TLO test in README. fixes #9

The test for model precision (MP) is based on the one-tailed, one-sample binomial test for each rater. In a multiple-rater situation, the p-values from all raters are combined using the Fisher's method (a.k.a. Fisher's omnibus test).

@@

The test for the median of TLO is based on a resampling under the null hypothesis method.

@@

One must notice that the two statistical tests are testing the bear minimum. A significant test only indicates the topic model performs better than random guess. It is not an indication of good topic interpretability. Also, one should use a very conservative significant level, e.g. $\alpha < 0.001$.

>>>>

The test for model precision (MP) is based on an one-tailed, one-sample binomial test for each rater. In a multiple-rater situation, the p-values from all raters are combined using the Fisher's method (a.k.a. Fisher's omnibus test).

@@

The test for the median of TLO is based on a permutation test.

@@

One must notice that the two statistical tests are testing the bear minimum. A significant test only indicates the topic model can make the rater(s) perform better than random guess. It is not an indication of good topic interpretability. Also, one should use a very conservative significant level, e.g. $\alpha < 0.001$.
